\documentclass{article}

\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathabx}
\usepackage{amsfonts}
\usepackage{enumitem}
\graphicspath{ {./images/} }
\usetikzlibrary{shapes}
\usepgfplotslibrary{polar}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{backgrounds}
\pgfplotsset{every axis/.append style={
                    axis x line=middle,    % put the x axis in the middle
                    axis y line=middle,    % put the y axis in the middle
                    axis line style={<->,color=blue}, % arrows on the axis
                    xlabel={$x$},          % default put x on x-axis
                    ylabel={$y$},          % default put y on y-axis
            }}
\newcommand{\numpy}{{\tt numpy}}    % tt font for numpy
\usepackage[utf8]{inputenc}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{remark}[example]{Remark}

\title{NP Hardness}
\author{MinSeok Song}
\date{}

\begin{document}
\maketitle 
\begin{itemize}
\item NP complete problems
\begin{itemize}
\item P:
all decision problems that can be solved in polynomial time.

\item NP
: all decision problems for which the proof of "yes" can be verified in polynomial time.

\item NP-Complete: Any other NP problems can be reduced to this in a polynomial time. (ex) 3-SAT(Boolean Satisfiability problem, aka 3-CNF~conjunctive normal form), proof in $http://www.cs.ecu.edu/karl/6420/spr16/Notes/NPcomplete/3sat.html$. !Not sure why SAT being reduced to 3-SAT proves this.

\item NP-hard: there exists NP-complete that can be reduced to this in a polynomial time. do not have to be decision problems, (ex) halting problem.

\begin{itemize}
\item picture: $https://www.geeksforgeeks.org/introduction-to-np-completeness/$
\end{itemize}
\end{itemize}
\item Example of NP-complete

1. Shortest vs. longest simple paths

2. Euler tour vs. hamiltonian cycle (visit each vertex only once)

3. 2CNF vs. 3CNF
\item If we can prove NP-complete in polynommial time, then we can prove NP in polynomial time. general belief is that NP-complete is not solvable in polynomial time.
\begin{itemize}
\item so, how do we prove that something is NP-complete? (p1051)
\end{itemize}





\end{itemize}

\end{document}